\chapter{Prototype Design}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION: System design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System design}
Show structural block diagram of the whole system and how the modules are connected
 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION: High level Design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{High level design}
Mainly for Application level, explain protocols and interation between components.\\
For each level, provides structural diagram of component connection and mention what actions are perform between them.
\subsection{Inputs/Outputs instruction design}
How are the inputs connected? How do they communicate with the micro (UART, Buffers, Queues)
When and when to send/receive instructions.\\
Instruction set tables with reasons for instruction size.
\subsection{External storage}
What action are performed on the storages? How is it structure?
\subsection{Alarm and Clock}
How is the time obtained?\\
When is time requested?\\
Why different RTCs?\\
Synchronization?\\
Alarm management.
\subsection{Visual outputs}
What application can have access to the visual outputs?\\
Defines the need for modes (normal, alarm, sunrise, sleep \ldots).\\
Pixels parameters?\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SECTION: Detailed design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Details design}
Provide schematics and pcb for each modules.
\subsection{Neopixels}
How do we program it (daisy chain, buffer).\\
\subsection{Screen}
How is it programed?\\
GUI?\\
Show screen and instruction sent.
\subsection{Android application}
How is it programed?\\
GUI?\\
Show screen and instruction sent.
\subsection{Bluetooth}
\subsection{Eeprom}
\subsection{External RTC}
\subsection{Internal RTC and Alarms}
