{\Large Abstract}\\
\hrule
\vskip 10mm

Studies made on human behavioural patterns have revealed the existence of ‘endogenous clocks’ that control the human circadian rhythm. Among these clocks, the master clock located in the suprachiasmatic nuclei is responsible for controlling the sleep-wake cycle, and it is influenced by light.\\

This project aims to create a device capable of generating light emission patterns which can produce both soporific and gentle awakening effects on humans, to control the human sleep-wake cycle in a more gentle manner that can have health benefits. The proposed device is planned as a type of alarm clock product, which can assist in the cure of sleep disorders. The product has been named the NeoPixel Sunrise Clock (NPSC) in consideration of the newly available NeoPixel LED technologies around which it is built.\\

The NPSC design is separated into three aspects: the hardware, the software and the mechanical design. The hardware design details the selection of components from which the device will be constructed in order to meet the light and other operational requirements. The mechanical design is paired with the hardware design to ensure that the device can fit in a 25 x 25 x 10cm$^3$ case. The software design consists of identifying the abstract modules and designing when required communication protocols between these modules. A significant mechanical design decision was for the device to use a ring consisting of 180 neopixels as the light source; it was furthermore chosen to incorporate external storage capacity and a real time clock used in the alarm functionality, as well as an onboard touchscreen for the user interface and the option to link to a smartphone application.\\

The system was tested using software unit tests and a logic analyser for the hardware assembly. The light source luminance, current drawn per colour and temperature rise were quantified during experiments. In testing it was found that the ring of neopixels performed well as the light source, performing above expectations. It emits light of 465-467nm wavelength with an illuminance above 30 lx on any objects placed at maximum of 1m at a maximum angle of 90 degrees to the normal of the ring surface.\\

With the NPSC functionalities fully implemented, the device could be used to provide personal lighting recommendation based on the user's sleep disorder.