\begin{thebibliography}{5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Circadian Rhythm 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GE Lighting, lighting and sleep
\bibitem{ge2014} General Electric Company, ``GE Lighting, lighting and sleep'', December 2014.
% Circadian and Light Effects on Human Sleepiness-Alertness
\bibitem{cir2014} C. Cajochen, S. L. Chellappa and C. Schmidt, ``Circadian and Light Effects on Human Sleepiness-Alertness'', \emph{Sleepiness and Human Impact Assessment}, pp. 9-22, 2014.
% Light, Melatonin and Sleep-Wake Cycle
\bibitem{lig1994} Gregory M. Brown, ``Light, Melatonin and Sleep-Wake Cycle'', \emph{Journal Psychriatry Neurosci}, {\bf vol. 19(5)}, pp. 345-353, Nov 1994.
% Blue light from light-emitting diodes elicits a dose-dependent suppression of melatonin in humans
\bibitem{bl2010} K. E. West, M. R. Jablonski, B. Warfield, K. S. Cecil, M. James, M. A. Ayers, J. Maida, C. Bowen, D. H. Sliney, M. D. Rollag, J. P. Hanifn and G. C. Brainard, ``Blue light from light-emitting diodes elicits a dose-dependent suppression of melatonin in humans'', \emph{Journal Appl Physiol}, {\bf vol. 110}, pp. 619-626, 16 Dec 2010.
% Action Spectrum for Melatonin Regulation in Humans: Evidence for a Novel Circadian Photoreceptor
\bibitem{ac2001} George C. Brainard, John P. Hanifin, Jeffrey M. Greeson, Brenda Byrne, Gena Glickman, Edward Gerner and Mark D. Rollag, ``Action Spectrum for Melatonin Regulation in Humans: Evidence for a Novel Circadian Photoreceptor'', \emph{Journal of Neuroscience}, {\bf vol. 21(16)}, pp. 6405-6412, 15 Au 2001.
% Phototransduction by Retinal Ganglion Cells That Set the Circadian Clock.
\bibitem{ph2002} Berson, D. M., F. A. Dunn, and M. Takao. ``Phototransduction by Retinal Ganglion Cells That Set the Circadian Clock.'' \emph{Science}, {\bf vol. 295}, pp. 1070-073, 2002.
% An action spectrum for melatonin suppression: evidence for a novel non-rod, non-cone photoreceptor system in humans
\bibitem{an2001} Kavita Thapan, Josephine Arendt and Debra J. Skene, ``An action spectrum for melatonin suppression: evidence for a novel non-rod, non-cone photoreceptor system in humans'', \emph{Journal of Physiology}, {\bf vol. 535.1}, pp.261-267, July 2001.
% Dose-response  relationship  for  light  intensity  and  ocular  and electroencephalographic  correlates  of  human  alertness
\bibitem{do2000} Christian  Cajochen*,  Jamie  M.  Zeitzer,  Charles  A.  Czeisler,  Derk-Jan  Dijk, ``Dose-response  relationship  for  light  intensity  and  ocular  and electroencephalographic  correlates  of  human  alertness'', \emph{Behavioural Brain Research }, {\bf vol. 115}, pp.75-83, May 2000.
% Early versus late bedtimes phase shift the human dim light melatonin rhythm despite a fixed morning lights on time
\bibitem{ea2004} Helen J. Burgess and Charmane I. Eastman, ``Early versus late bedtimes phase shift the human dim light melatonin rhythm despite a fixed morning lights on time'', \emph{Neurosci Lett.}, {\bf vol. 356(2)}, pp. 115–118, Feb 2004.
% Home Lighting Before Usual Bedtime Impacts Circadian Timing: A Field Study
\bibitem{ho2014} Helen J. Burgess and Thomas A. Molina, ``Home Lighting Before Usual Bedtime Impacts Circadian Timing: A Field Study'', \emph{Photochem Photobiol.}, {\bf vol. 90(3)}, pp. 723–726, 2014.
% Lighting for Health: LEDs in the New Age of Illumination
\bibitem{ho2014} US Department of Energy, ``Lighting for Health: LEDs in the New Age of Illumination'', \emph{Solid-State Lighting Technology Fact Sheet }, 2014.
% A Working Threshold for Acute Nocturnal Melatonin Suppression from “White”Light Sources used in Architectural Applications
\bibitem{aw2013} Mark S. Rea and Mariana G. Figueiro, ``A Working Threshold for Acute Nocturnal Melatonin Suppression from “White”Light Sources used in Architectural Applications'', \emph{Lighting Research Center, Rensselaer Polytechnic Institute, Troy, New York, USA}, 2013.
% Internal rhythms in humans
\bibitem{in1996} Derk-Jan Dijk, ``Internal rhythms in humans'', \emph{CELL \& DEVELOPMENTAL BIOLOGY}, {\bf vol. 7}, pp. 831-836, 1996.
% Scientific Background Discoveries of Molecular Mechanisms Controlling the Circadian Rhythm
\bibitem{sc2017} ``Scientific Background Discoveries of Molecular Mechanisms Controlling the Circadian Rhythm'', \emph{The Nobel Assembly at Karolinska Institutet}, 2017.
% Is sleep fundamentally different between mammalian species?
\bibitem{is1995} Tobler I., ``Is sleep fundamentally different between mammalian species?'', \emph{Behav Brain Res.}, {\bf vol. 69(1-2)}, pp. 35-41, Jul-Aug 1995.
% GE Sol
\bibitem{gesol} GE sol, [Online], available at: https://www.cbyge.com/products/sol
% Philips
\bibitem{philips} Philips, [Online], available at: https://www.usa.philips.com/c-p/HF3550\_60/discontinued-wake-up-light/overview
% Therapeutics for Circadian Rhythm Sleep Disorders
\bibitem{th2010} Ehren R. Dodson and Phyllis C Zee, ``Therapeutics for Circadian Rhythm Sleep Disorders'', \emph{Sleep Med Clin}, \textbf{vol. 5(4)}, pp. 701-715, Dec 2010.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Microcontrollers
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% How Microcontrollers Work
\bibitem{ho2000} Marshall Brain,``How Microcontrollers Work'',\emph{HowStuffWorks.com}[Online] ,available at: http://electronics.howstuffworks.com/microcontroller1.htm, 1 Apr 2000.
% Arduino Due Specifications
\bibitem{arduino} ``Arduino Due Specifications'', \emph{Arduino}, [Online], available at: https://store.arduino.cc/arduino-due
% Intel Edison Specifications
\bibitem{intel} ``Intel Edison Specifications'', \emph{Intel}, [Online], available at: https://cdn-shop.adafruit.com/datasheets/EdisonDatasheet.pdf
% Arduino Due Specifications
\bibitem{raspberry} ``Raspberry Pi Zero Specifications'', \emph{Raspberry Pi}, [Online], available at: https://www.raspberrypi.org/products/raspberry-pi-zero-w/
% Arduino Due Specifications
\bibitem{stm} ``STM32F407VGT6 Specifications'', \emph{STM microelectronics}, [Online], available at: http://www.st.com/en/microcontrollers/stm32f407-417.html?querycriteria=productId=LN11

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Storage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Serial EEPROM Solutions vs. Parallel Solutions
\bibitem{serialvsparallel} Tom Tyson, ``Serial EEPROM Solutions vs. Parallel Solutions'', \emph{Memory Products Division, Microchip}, [Online], available at: http://ecee.colorado.edu/~mcclurel/microchipan551.pdf
% Basic Serial EEPROM Operation
\bibitem{serialoperation} Steve Drehobl, ``Basic Serial EEPROM Operation'', \emph{Memory Products Division, Microchip}, [Online], available at: http://ecee.colorado.edu/~mcclurel/man536.pdf
% Embedded EEPROM Speed Optimization Using System Power Supply Resources
\bibitem{embeddedeeprom} Jean-Michel DagaCaroline, PapaixMarylene CombeEmmanuel, RacapeVincent Sialelli, ``Embedded EEPROM Speed Optimization Using System Power Supply Resources'', \emph{Lecture Notes in Computer Science}, \textbf{vol. 3254}. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wireless communication
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bluetooth in wireless communication
\bibitem{bluetooth} K. V. S. S. S. S. Sairam and N. Gunasekaran and S. R. Redd, ``Bluetooth in wireless communication'', \emph{IEEE Communications Magazine}, \textbf{vol. 40(6)}, pp. 90-96, Jun 2002. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bluetooth
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Resistive Touch Screen
\bibitem{resistivetouch} ``Resistive Touch Screen'', \emph{Baanto},[Online], available at: http://baanto.com/resistive-touch-screen-technology
% Capacitive Touch Screen
\bibitem{capacitivetouch} ``Capacitive Touch Screen'', \emph{Baanto},[Online], available at: http://baanto.com/capacitive-touch-screen

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Communications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SPI
\bibitem{spi} ``Serial Peripheral Interface (SPI) '', \emph{Sparkfun},[Online], available at: https://learn.sparkfun.com/tutorials/serial-peripheral-interface-spi
% UART
\bibitem{uart} `` Serial Communication '', \emph{Sparkfun},[Online], available at: https://learn.sparkfun.com/tutorials/serial-communication 
% I2C
\bibitem{i2c} ``I2C'', \emph{Sparkfun},[Online], available at: https://learn.sparkfun.com/tutorials/i2c


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PCB Design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Generic Standard on Printed Board Design
\bibitem{pcb_design} ``Generic Standard on Printed Board Design'', \emph{ASSOCIATION CONNECTING
ELECTRONICS INDUSTRIES},[Online], available at: http://www.sphere.bc.ca/class/downloads/ipc\_2221a-pcb\%20standards.pdf
% Trace Width Website Calculator
\bibitem{pcb_track_width} Advanced Circuits, ``Trace Width Website Calculator'', [Online] available at: http://www.4pcb.com/trace-width-calculator.html


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Programming
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Programming in C : A complete intorduction to the C programming language
\bibitem{c_programming} Stephen G. Kochan, ``Programming in C : A complete intorduction to the C programming language, Third Edition''.
% Java: The complete reference, Seventh Edition
\bibitem{java_programming} Herbert Schildt, ``Java: The complete reference, Seventh Edition''.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Light
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Programming in C : A complete intorduction to the C programming language
\bibitem{lighting} Energy Saver, ``Type of lighting'', \emph{U.S Department of Energy}, [Onile] available at: https://energy.gov/energysaver/types-lighting.
% Modern Optical Engineering
\bibitem{optical} Warren J. Smith, ``Modern Optical Engineering: The Design of Optical Systems''


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Software tool
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Features
\bibitem{atollic} Atollic TrueSTUDIO, ``Features'', \emph{Atollic TrueSTUDIO}, [Onile] available at: https://atollic.com/truestudio/features/
% Features
\bibitem{nextion} Nextion, ``Features'', \emph{Nextion}, [Onile] available at: https://nextion.itead.cc/
% Features
\bibitem{android} Android, ``Everything you need to build on Android'', \emph{Android}, [Onile] available at: https://developer.android.com/studio/features.html
% paper
\bibitem{ref} authors, ``Paper'', \emph{Journal}, \textbf{vol.}, pp. 
\end{thebibliography}
