\chapter{User manual}
\textbf{Version: 1.0}\\
This user manual is written for the first prototype of the NPSC. Not all applications have been successfully implemented for this prototype as a result, this manual only provides information on the working modules.

\section{Requirements}
To use the NPSC, the user must have the following items.
\begin{itemize}
	\item NPSC prototype.
	\item A USB mini B cable to power the STM32F4 Discovery board.
	\item A 5V@10A power supply for the visual module (Ring, Time \& Weekday).
	\item A 5V@500mA power supply for the STM32F4 Discovery board.
	\item A computer running the software listed in \ref{software_setup} (for developers only).
\end{itemize}

\section{How to use it?}
\subsection{User mode}
The user must power the NPSC by providing power to the visual outputs and the STM (use the list of requirement for guidance).\\
The NPSC is controlled by two devices, the android application or the onboard touchscreen. The home screen displays the time and date information as well as the coming alarms.\\
The following functionalities are found on the menu:
\begin{itemize}
	\item Clock: The clock information including, time, date can be updated from the clock screen.
	\item Alarm: The alarm screen displays the alarm saved. Each alarm can be updated and set. 
\end{itemize}

\subsection{Developer mode}
The STM32F4 Discovery board should be connected to a computer to program the STM. The screen would have to be removed from the NPSC case in order to be programmed.

\section{Any issues?}
Please send an email to kylekojey@gmail.com for any queries related to the NPSC.