\chapter{Project artefact}


\section{Git repository}
The project is under version control and is found on \href{https://github.com/Kojey/NPSC}{github}.\\
\subsection{Branches}
The repository has five main branches: 
\begin{itemize}
	\item \textbf{master}: This is the master branch running on the NPSC hardware.
	\item \textbf{hardware}: All hardware modifications are done on this branches prior any merge to master. 
	\item \textbf{software}: All software modifications are done on this branches prior any merge to master. This include the STM, Nextion, Android application and arduino testing code. 
	\item \textbf{mechanical}: All mechanical modifications are done on this branches prior any merge to master. 
	\item \textbf{report}: All modification related to the report writing are done on this branches prior any merge to master. 
\end{itemize}

\subsubsection{Commit format}
For anyone willing to contribute to the project, please adhere to the commit format shown in listing \ref{code:commit}:\\
\begin{lstlisting}[language=C,caption=Commit format, label=code:commit]
<branch>-<modification type>: <Summary of the change>

<details on changes performed ...>
<details on changes performed ...>
...
<more detail on changes>
\end{lstlisting}

\section{Project structure}
\subsection{Overview}
\subsubsection{Project tree}
\begin{itemize}
	\item \textbf{bibliography}: All papers used in the litterature review.
	\item \textbf{ethics}: All ethics related documents.
	\item \textbf{experiments}: All experiments codes and results performed on the NPSC.
	\item \textbf{miscellaneous}: Calculation done to find illuminance emitted by the neopixels.
	\item \textbf{mechanical}: All mechanical documents used in the design.
	\item \textbf{report}: The latex report.
	\item \textbf{hardware}: \label{npsc_harware}
	\begin{itemize}
		\item \textbf{design}: All schematics and PCB designed.
		\item \textbf{documentation}: All datasheets for the components used.
		\item \textbf{manufacturing}: All Gerber files required for the PCBs manufacturing.
	\end{itemize}
	\item \textbf{software}: \label{npsc_software}
	\begin{itemize}
		\item \textbf{code}:
		\begin{itemize}
			\item \textbf{android}: The APK used for the android application.
			\item \textbf{arduino}: All android code used to do prior tests on the hardware module.
			\item \textbf{master}: The NPSC software library and the Atolic TrueSTUDIO project settings.
			\item \textbf{screen}: The nextion code in HMI format and fonts used.
		\end{itemize}
		\item \textbf{documentation}:
		\begin{itemize}
			\item \textbf{api/master/html}: The html and css format of the NPSC's API (open the index.html file)
			\item instruction set in excel format 
		\end{itemize}
		\item \textbf{graphics}: All graphics used for the Nextion touchscreen
		\item \textbf{templates}: Doxygen templates used for header and c files.
	\end{itemize}
\end{itemize}


\subsubsection{NPSC library tree}
\begin{itemize}
	\item \textbf{Application}: Contains all files used for the application modules.
	\item \textbf{Framework}: Contains all files used for the framework modules.
	\item \textbf{IntegrationTest}: Contains all files used for the integration tests.
	\item \textbf{UnitTest}: Contains all files used for the unit tests.
	\item \textbf{Utilities}: Contains all files used for the Utilities.
\end{itemize}